Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-11-28 concurrency/CPP 2024/paper.tex
distinguished nodeboxrep/Ref from in_tree/inFP
I'd somehow collapsed the two in my descriptions.

\newcommand\dboxed[1]{\dbox{\ensuremath{#1}}}
\newcommand{\master}[2]{\ensuremath{\mathrm{Master}_{#1}(#2)}}
\newcommand{\snap}[1]{\ensuremath{\mathrm{Snapshot}(#1)}}
\newcommand{\ghost}[2]{\ensuremath{\dboxed{#1}^{#2}}}
\newcommand{\us}{$\mu$s}
\newcommand{\gnamety}{\ensuremath{\mathsf{gname}}}
\newcommand{\treerep}{\ensuremath{\mathsf{Abs}}}
\newcommand{\nodeboxrep}{\ensuremath{\mathsf{Ref }}}
\newcommand{\lockinv}{\ensuremath{\mathsf{lock\_inv}}}
\newcommand{\infp}{\ensuremath{\mathsf{Ref }}}

@@

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{XXXXXXX.XXXXXXX}
\acmYear{2024}
\copyrightyear{2024}
\acmSubmissionID{}
\acmISBN{}
%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[CPP '24]{Proceedings of the 13th ACM SIGPLAN International Conference on Certified Programs and Proofs}{Jan 15--16, 2024}{London, United Kingdom}
\acmBooktitle{Proceedings of the 13th ACM SIGPLAN International Conference on Certified Programs and Proofs (CPP '24), Jan 15--16, 2024, London, United Kingdom}

@@

We prove correctness of the template by showing that \lstinline{traverse}, \\ \lstinline{insert}, etc. meet logically atomic specifications describing their effects on the data structure. These specifications are defined in terms of assertions $\nodeboxrep$, representing a client thread's handle to the data structure, and $\treerep$, representing the data structure's abstract state. Holding $\nodeboxrep(n)$ for a node $n$ should allow us to acquire the lock on $n$, which in turn gives us access to the contents of the node. Formally, we need to know that the following triples hold:

\begin{minipage}{.2\textwidth}
	\centering
\begin{mathpar}
	{\color{specblue}\left\langle \nodeboxrep \left(n\right) \ |\ \treerep\ (m) \right\rangle}\ 
	\vspace{-0.8em} \\ \texttt{acquire}\left(n\texttt{->lock}\right)\  \vspace{-0.8em}  \\ {\color{specblue}\left\langle \nodeboxrep(n) \ast \mathsf{R}(n) \ |\ \treerep\ (m)\right\rangle}
\end{mathpar}
\end{minipage}
\begin{minipage}{.28\textwidth}
		\centering
\begin{mathpar}
	{\color{specblue}\left\langle \nodeboxrep \left(n\right) \ |\ \treerep\ (m) \right\rangle}\ 
	\vspace{-0.8em} \\ \texttt{acquire}\left(n\texttt{->lock}\right)\  \vspace{-0.8em}  \\ {\color{specblue}\left\langle \nodeboxrep(n) \ast \mathsf{R}(n) \ |\ \treerep\ (m)\right\rangle}
\end{mathpar}
\end{minipage} \\

In other words, $\nodeboxrep(n)$ is sufficient to guarantee that node $n$ is in the abstract state of the data structure and its lock protects associated resources $\mathsf{R}(n)$, the \emph{lock invariant} for the node. 
%In this case, $\mathsf{R}$ contains the contents of the node (i.e., the \lstinline{node} struct contained inside the \lstinline{node_t} struct of \lstinline{n}).

%\wm{The fonts are still off here---for instance, p, n, and n' are mathematical variables, not references to the C code. Fix if we have time.}
The \lstinline{traverse} function can then be specified as follows:
%\than{Try to avoid using specific name of $\mathrm{tree\_rep}$ for public condition, I suggested to use $\mathrm{Node}$ for generic purpose.} 
\begin{mathpar}
{ \color{specblue}
	\fforall \  m. \ \scaleleftright[1.4ex]{\langle}
	{\begin{array}{l}
			\texttt{pn} \mapsto (p, n) \ \ast \ 
			\nodeboxrep(n)  \ast \ \mathsf{R}(n) 
		\end{array}  
		\Big \vert  \treerep\ (m)
	}  
	{\rangle}
}
\vspace{-6pt}\\
\vspace{-6pt}\texttt{traverse(pn, k)} \\
{ \color{specblue}
 \scaleleftright[1.4ex]{\langle}
{\begin{array}{l}
		\mathit{res}. \exists \  n', v, \mathsf{range}. \\ 
		\ \ \ \ \ \  \texttt{pn} \mapsto \left(n', n'\right) \ast  \nodeboxrep\left(n'\right) \ast\ \texttt{k} \in \mathsf{range}\ \ast \ 
		\\ 
		\ \ \ \ \ \ \mathsf{if} \ \mathit{res}  \ \mathsf{then}  \ \mathsf{node\_contents}(n', \cdot, \mathsf{range}) \ 
		\\ 
		\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mathsf{else} \ \mathsf{node\_contents}(n', (\texttt{k}, v), \mathsf{range})
\end{array}  
\Bigg \vert \treerep\ (m)
}  
{\rangle}
}
\end{mathpar}

The local precondition of \lstinline{traverse} includes both the node handle $\nodeboxrep(n)$ and its contents $\mathsf{R}(n)$, indicating that a thread should already hold $n$'s lock before calling \lstinline{traverse}. The output of \lstinline{traverse} is a new node $n'$ in the data structure such that the key \texttt{k} falls within the range of $n'$. The local postcondition then includes the handle of the new node $\nodeboxrep(n')$, its contents $\mathsf{R}(n')$, and a Boolean variable $\mathit{res}$ indicating whether \lstinline{traverse} found an empty node or a node with key \lstinline{k}.

@@

The key to the correctness of the \texttt{traverse} function is the loop invariant for the top-level loop, which expresses that in each iteration, \lstinline{traverse} holds the lock on a node that has \lstinline{k} in its range:
\begin{align*}\mathsf{traverse\_inv}(\texttt{pn}, \texttt{k}) \triangleq \\ \exists \ p, n, c, \mathsf{range}.\ &\texttt{pn} \mapsto (p, n) \ast \texttt{k} \in \mathsf{range}\ \ast \ \\  \nodeboxrep(n)  \ \ast \  &\mathsf{node\_contents}(n, c, \mathsf{range})
\end{align*}

\begin{figure*}[!ht]
	$\color{specblue}
	\fforall \  m. \left\langle \texttt{pn} \mapsto (p, n) \ \ast \ 
	\nodeboxrep(n)  \ \ast \ \mathsf{R}(n) \ \big| \ \treerep\ (m) \
	\right\rangle$
		\begin{minipage}{0.9\textwidth}
			\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_lock_traverse.c}
		\end{minipage}
	$\color{specblue}
	\left\langle \mathit{res}. \ \exists \  n', v.
	\begin{array}{l} \texttt{pn} \mapsto (n', n') \ \ast \nodeboxrep(n') \ \ast\ \texttt{k} \in \mathsf{range}\ \ast\ 
		\\ 
		\mathsf{if} \ \mathit{res} \ \mathsf{then} \ \mathsf{node\_contents}(n', \cdot, \mathsf{range}) \ 
		\\ \ \ \ \ \ \ \ \ \ \mathsf{else} \ \mathsf{node\_contents}(n', (\texttt{k}, v), \mathsf{range})
	\end{array}
	\ \Bigg| \treerep\ (m) \
	\right\rangle$
	\caption{Proof outline of the lock-coupling \texttt{traverse} function}
	\label{proof_lock_traverse}
\end{figure*}

@@

\subsubsection{Verifying the Give-Up Template}
\label{traverse_proof_giveup}
The give-up template's \texttt{traverse} specification is almost the same as in the lock-coupling template, except that the caller does not need to hold any locks before calling it, so the invariant $\mathsf{R}$ does not appear in the precondition:
\begin{mathpar}
	{ \color{specblue}
		\fforall \  m. \ \scaleleftright[1.4ex]{\langle}
		{\begin{array}{l}
				\texttt{pn} \mapsto (p, n) \ast  
				\nodeboxrep(n)   
			\end{array}  
			\Big \vert  \treerep\ (m)
		}  
		{\rangle}
	}
	\vspace{-6pt}\\
	\vspace{-6pt}\texttt{traverse(pn, k)} \\
	{ \color{specblue}
		\scaleleftright[1.4ex]{\langle}
		{\begin{array}{l}
				\mathit{res}. \exists \  n', v, \mathsf{range}. \\ 
				\ \ \ \ \ \  \texttt{pn} \mapsto \left(n', n'\right) \ast  \nodeboxrep\left(n'\right) \ast \texttt{k} \in \mathsf{range} \ \ast 
				\\ 
				\ \ \ \ \ \ \mathsf{if} \ \mathit{res}  \ \mathsf{then}  \ \mathsf{node\_contents}(n', \cdot, \mathsf{range}) \ 
				\\ 
				\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mathsf{else} \ \mathsf{node\_contents}(n', (\texttt{k}, v), \mathsf{range})
			\end{array}  
			\Bigg \vert \treerep\ (m)
		}  
		{\rangle}
	}
\end{mathpar}

@@

Next, we define the loop invariant for the give-up template's \texttt{traverse} function:
\begin{align*} &\mathsf{traverse\_inv}(\texttt{pn}) \triangleq \\  & \ \ \ \ \ \ \ \ \exists \ p, r, n.\ \texttt{pn} \mapsto (p, n) \ast  \infp (r) \ast \infp (n)
\end{align*}
Unlike the lock-coupling case, we do not hold any locks between iterations of the loop body, and we do not maintain the fact that \lstinline{k} is in the range of the current node (we must check this later with \lstinline{inRange}). Instead, we keep a reference $\infp(r)$ to the root node, so that we can return to it if an \lstinline{inRange} check fails.

With this invariant in hand, the proof of \texttt{traverse} proceeds as follows. We begin by using the $\infp$ predicate to acquire the lock on \lstinline{pn->n} (line 4 in Figure \ref{traverse_giveup_b}). We then call \lstinline{inRange} to check whether we are still on the path to a node that can hold \lstinline{k}. If the check fails (lines 18-20), we immediately release the lock and start over from the root node $r$. Otherwise, we proceed as in the lock-coupling template: if the current node's contents are \texttt{NULL}, we have found the empty node where \texttt{k} belongs (and can satisfy the postcondition); if \texttt{findNext} returns 0, we have found the node containing \texttt{k} (and can satisfy the postcondition); otherwise, we release the lock and re-establish $\mathsf{traverse\_inv}$ for the new node indicated by \texttt{findNext}. In this case, we once again hold no locks, and have only the $\infp$ assertion indicating that the new node is in the data structure. % and add the additional predicate $\texttt{k} \in \texttt{range(n)}$ in the \texttt{then} of \texttt{inRange}. Similar to the proof of the lock-coupling template's \texttt{traverse}, the traversal stops when it reaches the base case, which occurs when the current node is \texttt{NULL} (line 8 in Figure \ref{traverse_giveup_b}). At this point, we can prove the post-condition using the specification, which indicates that $\texttt{k} \in \texttt{range(n')} \ast \texttt{pn->n'->t} = \texttt{NULL}$.

@@

\section{Proof Outlines for Templates (Sections \ref{traverse_proof_lock} and \ref{traverse_proof_giveup})}
\label{sec:apd_proof}
Below are proof outlines for the \texttt{traverse} function for the give-up template (Figure \ref{proof_giveup_traverse}) as well as the \texttt{insert} function for both templates. The complete proofs can be found in our Coq mechanization (see Section \ref{proof_mech}).
\begin{figure*}[h]
	$\color{specblue}
	\fforall \  m. \left\langle
	\begin{array}{c}
		\texttt{pn} \mapsto (p, n)  \ast  \nodeboxrep(n)  \big| \ \treerep\ (m)
	\end{array}
	\right\rangle$
	\begin{minipage}{0.9\textwidth}
	\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_giveup_traverse.c}
	\end{minipage}
	$\color{specblue}
	\left\langle \mathit{res}. \ \exists \  n', v.
	\begin{array}{l} \texttt{pn} \mapsto (n', n') \ast \nodeboxrep(n') \ \ast \ \texttt{k} \in \mathsf{range}\ \ast \ 
		\\ 
		(\mathsf{if} \ \mathit{res} \ \mathsf{then} \ \mathsf{node\_contents}(n', \cdot, \mathsf{range}) \ 
		\\ \ \ \ \ \ \ \ \ \ \mathsf{else} \ \mathsf{node\_contents}(n', (\texttt{k}, v), \mathsf{range}))
	\end{array}
	\ \Bigg| \ \treerep\ (m) \
	\right\rangle$
	\caption{Proof outline of the give-up \texttt{traverse} function}
	\label{proof_giveup_traverse}
\end{figure*}

>>>>

\newcommand\dboxed[1]{\dbox{\ensuremath{#1}}}
\newcommand{\master}[2]{\ensuremath{\mathrm{Master}_{#1}(#2)}}
\newcommand{\snap}[1]{\ensuremath{\mathrm{Snapshot}(#1)}}
\newcommand{\ghost}[2]{\ensuremath{\dboxed{#1}^{#2}}}
\newcommand{\us}{$\mu$s}
\newcommand{\gnamety}{\ensuremath{\mathsf{gname}}}
\newcommand{\treerep}{\ensuremath{\mathsf{Abs}}}
\newcommand{\nodeboxrep}{\ensuremath{\mathsf{Ref }}}
\newcommand{\lockinv}{\ensuremath{\mathsf{lock\_inv}}}
\newcommand{\inFP}{\ensuremath{\mathsf{In }}}

@@

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{rightsretained}
\acmDOI{XXXXXXX.XXXXXXX}
\acmYear{2024}
\copyrightyear{2024}
\acmSubmissionID{}
\acmISBN{}
%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[CPP '24]{Proceedings of the 13th ACM SIGPLAN International Conference on Certified Programs and Proofs}{Jan 15--16, 2024}{London, United Kingdom}
\acmBooktitle{Proceedings of the 13th ACM SIGPLAN International Conference on Certified Programs and Proofs (CPP '24), Jan 15--16, 2024, London, United Kingdom}

@@

We prove correctness of the template by showing that \lstinline{traverse}, \\ \lstinline{insert}, etc. meet logically atomic specifications describing their effects on the data structure. These specifications are defined in terms of assertions $\nodeboxrep$, representing a client thread's handle to the data structure, and $\treerep$, representing the data structure's abstract state. We also have an assertion $\inFP(n)$ that serves as a reference to an individual node; $\nodeboxrep$ should include, at minimum, the $\inFP$ assertion for the root node.
Holding $\inFP(n)$ for a node $n$ should allow us to acquire the lock on $n$, which in turn gives us access to the contents of the node. Formally, we need to know that the following triples hold:

\begin{minipage}{.2\textwidth}
	\centering
\begin{mathpar}
	{\color{specblue}\left\langle \inFP \left(n\right) \ |\ \treerep\ (m) \right\rangle}\ 
	\vspace{-0.8em} \\ \texttt{acquire}\left(n\texttt{->lock}\right)\  \vspace{-0.8em}  \\ {\color{specblue}\left\langle \inFP(n) \ast \mathsf{R}(n) \ |\ \treerep\ (m)\right\rangle}
\end{mathpar}
\end{minipage}
\begin{minipage}{.28\textwidth}
		\centering
\begin{mathpar}
	{\color{specblue}\left\langle \inFP \left(n\right) \ast \mathsf{R}(n) \ |\ \treerep\ (m) \right\rangle}\ 
	\vspace{-0.8em} \\ \texttt{release}\left(n\texttt{->lock}\right)\  \vspace{-0.8em}  \\ {\color{specblue}\left\langle \inFP(n) \ |\ \treerep\ (m)\right\rangle}
\end{mathpar}
\end{minipage} \\

In other words, $\inFP(n)$ is sufficient to guarantee that node $n$ is in the abstract state of the data structure and its lock protects associated resources $\mathsf{R}(n)$, the \emph{lock invariant} for the node. 
%In this case, $\mathsf{R}$ contains the contents of the node (i.e., the \lstinline{node} struct contained inside the \lstinline{node_t} struct of \lstinline{n}).

%\wm{The fonts are still off here---for instance, p, n, and n' are mathematical variables, not references to the C code. Fix if we have time.}
The \lstinline{traverse} function can then be specified as follows:
%\than{Try to avoid using specific name of $\mathrm{tree\_rep}$ for public condition, I suggested to use $\mathrm{Node}$ for generic purpose.} 
\begin{mathpar}
{ \color{specblue}
	\fforall \  m. \ \scaleleftright[1.4ex]{\langle}
	{\begin{array}{l}
			\texttt{pn} \mapsto (p, n) \ \ast \ 
			\inFP(n)  \ast \ \mathsf{R}(n) 
		\end{array}  
		\Big \vert  \treerep\ (m)
	}  
	{\rangle}
}
\vspace{-6pt}\\
\vspace{-6pt}\texttt{traverse(pn, k)} \\
{ \color{specblue}
 \scaleleftright[1.4ex]{\langle}
{\begin{array}{l}
		\mathit{res}. \exists \  n', v, \mathsf{range}. \\ 
		\ \ \ \ \ \  \texttt{pn} \mapsto \left(n', n'\right) \ast  \inFP\left(n'\right) \ast\ \texttt{k} \in \mathsf{range}\ \ast \ 
		\\ 
		\ \ \ \ \ \ \mathsf{if} \ \mathit{res}  \ \mathsf{then}  \ \mathsf{node\_contents}(n', \cdot, \mathsf{range}) \ 
		\\ 
		\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mathsf{else} \ \mathsf{node\_contents}(n', (\texttt{k}, v), \mathsf{range})
\end{array}  
\Bigg \vert \treerep\ (m)
}  
{\rangle}
}
\end{mathpar}

The local precondition of \lstinline{traverse} includes both the node handle $\inFP(n)$ and its contents $\mathsf{R}(n)$, indicating that a thread should already hold $n$'s lock before calling \lstinline{traverse}. The output of \lstinline{traverse} is a new node $n'$ in the data structure such that the key \texttt{k} falls within the range of $n'$. The local postcondition then includes the handle of the new node $\inFP(n')$, its contents $\mathsf{R}(n')$, and a Boolean variable $\mathit{res}$ indicating whether \lstinline{traverse} found an empty node or a node with key \lstinline{k}.

@@

The key to the correctness of the \texttt{traverse} function is the loop invariant for the top-level loop, which expresses that in each iteration, \lstinline{traverse} holds the lock on a node that has \lstinline{k} in its range:
\begin{align*}\mathsf{traverse\_inv}(\texttt{pn}, \texttt{k}) \triangleq \\ \exists \ p, n, c, \mathsf{range}.\ &\texttt{pn} \mapsto (p, n) \ast \texttt{k} \in \mathsf{range}\ \ast \ \\  \inFP(n)  \ \ast \  &\mathsf{node\_contents}(n, c, \mathsf{range})
\end{align*}

\begin{figure*}[!ht]
	$\color{specblue}
	\fforall \  m. \left\langle \texttt{pn} \mapsto (p, n) \ \ast \ 
	\inFP(n)  \ \ast \ \mathsf{R}(n) \ \big| \ \treerep\ (m) \
	\right\rangle$
		\begin{minipage}{0.9\textwidth}
			\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_lock_traverse.c}
		\end{minipage}
	$\color{specblue}
	\left\langle \mathit{res}. \ \exists \  n', v.
	\begin{array}{l} \texttt{pn} \mapsto (n', n') \ \ast \inFP(n') \ \ast\ \texttt{k} \in \mathsf{range}\ \ast\ 
		\\ 
		\mathsf{if} \ \mathit{res} \ \mathsf{then} \ \mathsf{node\_contents}(n', \cdot, \mathsf{range}) \ 
		\\ \ \ \ \ \ \ \ \ \ \mathsf{else} \ \mathsf{node\_contents}(n', (\texttt{k}, v), \mathsf{range})
	\end{array}
	\ \Bigg| \treerep\ (m) \
	\right\rangle$
	\caption{Proof outline of the lock-coupling \texttt{traverse} function}
	\label{proof_lock_traverse}
\end{figure*}

@@

\subsubsection{Verifying the Give-Up Template}
\label{traverse_proof_giveup}
The give-up template's \texttt{traverse} specification is almost the same as in the lock-coupling template, except that the caller does not need to hold any locks before calling it, so the invariant $\mathsf{R}$ does not appear in the precondition:
\begin{mathpar}
	{ \color{specblue}
		\fforall \  m. \ \scaleleftright[1.4ex]{\langle}
		{\begin{array}{l}
				\texttt{pn} \mapsto (p, n) \ast  
				\inFP(n)   
			\end{array}  
			\Big \vert  \treerep\ (m)
		}  
		{\rangle}
	}
	\vspace{-6pt}\\
	\vspace{-6pt}\texttt{traverse(pn, k)} \\
	{ \color{specblue}
		\scaleleftright[1.4ex]{\langle}
		{\begin{array}{l}
				\mathit{res}. \exists \  n', v, \mathsf{range}. \\ 
				\ \ \ \ \ \  \texttt{pn} \mapsto \left(n', n'\right) \ast  \inFP\left(n'\right) \ast \texttt{k} \in \mathsf{range} \ \ast 
				\\ 
				\ \ \ \ \ \ \mathsf{if} \ \mathit{res}  \ \mathsf{then}  \ \mathsf{node\_contents}(n', \cdot, \mathsf{range}) \ 
				\\ 
				\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \mathsf{else} \ \mathsf{node\_contents}(n', (\texttt{k}, v), \mathsf{range})
			\end{array}  
			\Bigg \vert \treerep\ (m)
		}  
		{\rangle}
	}
\end{mathpar}

@@

Next, we define the loop invariant for the give-up template's \texttt{traverse} function:
\begin{align*} &\mathsf{traverse\_inv}(\texttt{pn}) \triangleq \\  & \ \ \ \ \ \ \ \ \exists \ p, r, n.\ \texttt{pn} \mapsto (p, n) \ast  \inFP (r) \ast \inFP (n)
\end{align*}
Unlike the lock-coupling case, we do not hold any locks between iterations of the loop body, and we do not maintain the fact that \lstinline{k} is in the range of the current node (we must check this later with \lstinline{inRange}). Instead, we keep a reference $\inFP(r)$ to the root node, so that we can return to it if an \lstinline{inRange} check fails.

With this invariant in hand, the proof of \texttt{traverse} proceeds as follows. We begin by using the $\inFP$ predicate to acquire the lock on \lstinline{pn->n} (line 4 in Figure \ref{traverse_giveup_b}). We then call \lstinline{inRange} to check whether we are still on the path to a node that can hold \lstinline{k}. If the check fails (lines 18-20), we immediately release the lock and start over from the root node $r$. Otherwise, we proceed as in the lock-coupling template: if the current node's contents are \texttt{NULL}, we have found the empty node where \texttt{k} belongs (and can satisfy the postcondition); if \texttt{findNext} returns 0, we have found the node containing \texttt{k} (and can satisfy the postcondition); otherwise, we release the lock and re-establish $\mathsf{traverse\_inv}$ for the new node indicated by \texttt{findNext}. In this case, we once again hold no locks, and have only the $\inFP$ assertion indicating that the new node is in the data structure. % and add the additional predicate $\texttt{k} \in \texttt{range(n)}$ in the \texttt{then} of \texttt{inRange}. Similar to the proof of the lock-coupling template's \texttt{traverse}, the traversal stops when it reaches the base case, which occurs when the current node is \texttt{NULL} (line 8 in Figure \ref{traverse_giveup_b}). At this point, we can prove the post-condition using the specification, which indicates that $\texttt{k} \in \texttt{range(n')} \ast \texttt{pn->n'->t} = \texttt{NULL}$.

@@

\section{Proof Outlines for Templates (Sections \ref{traverse_proof_lock} and \ref{traverse_proof_giveup})}
\label{sec:apd_proof}
Below are proof outlines for the \texttt{traverse} function for the give-up template (Figure \ref{proof_giveup_traverse}) as well as the \texttt{insert} function for both templates. The complete proofs can be found in our Coq mechanization (see Section \ref{proof_mech}).
\begin{figure*}[h]
	$\color{specblue}
	\fforall \  m. \left\langle
	\begin{array}{c}
		\texttt{pn} \mapsto (p, n)  \ast  \inFP(n)  \big| \ \treerep\ (m)
	\end{array}
	\right\rangle$
	\begin{minipage}{0.9\textwidth}
	\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_giveup_traverse.c}
	\end{minipage}
	$\color{specblue}
	\left\langle \mathit{res}. \ \exists \  n', v.
	\begin{array}{l} \texttt{pn} \mapsto (n', n') \ast \inFP(n') \ \ast \ \texttt{k} \in \mathsf{range}\ \ast \ 
		\\ 
		(\mathsf{if} \ \mathit{res} \ \mathsf{then} \ \mathsf{node\_contents}(n', \cdot, \mathsf{range}) \ 
		\\ \ \ \ \ \ \ \ \ \ \mathsf{else} \ \mathsf{node\_contents}(n', (\texttt{k}, v), \mathsf{range}))
	\end{array}
	\ \Bigg| \ \treerep\ (m) \
	\right\rangle$
	\caption{Proof outline of the give-up \texttt{traverse} function}
	\label{proof_giveup_traverse}
\end{figure*}
